SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-30 2017-Xudong-SMT/ActaInformatica.tex
merge proof2 and simon

When the pNets contains no assignment, there is no need for the last
filtering step, so $L1_{sat}=L1_{reach}$ and $L2_{sat}=L2_{reach}$.
We want to prove that $L1_{reach}=L2_{reach}$, that will imply
the equality of the 2 open automata.

\medskip
Let $S=\ostate{\overline{s}}=\ostate{\{s_{i}\}^{i\in Leaves(pn)}}$
range over the global states $States(L0)$, 
The only difference between the main loops of the algorithms is that 
algorithm~\ref{alg3} only retains the satisfiable OTs (line 6-7), so 
algorithm~\ref{alg3} computes less transitions than
algorithm~\ref{alg1}. Formaly $L2_{reach}\subseteq  L2_{sat} \subseteq L0$, and as a consequence $States(L2_{reach})\subseteq  States(L0)$, so we have:\\
\centerline{$\forall \ostate{\overline{u}}\in States(L2_{reach}), \exists\ostate{\overline{t}}\in States(L0), \ostate{\overline{t}}=\ostate{\overline{u}}$}

@@

\medskip
We will prove by induction on the distance from the original state,
that $\forall S \in L0. S \in States(L2_{reach}) \land |S|_{l2_{reach}}=n => S
\in States(L1_{reach})$, and vice-versa.

  The initial property is trivial, for $n=0$, both state sets of
  distance zero are reduced to $S_0$.

  Suppose our property is true for distance $n$, and
  suppose $|S|_{L2_{reach}}=n+1$, then there exist a chain
  $S_0\xrightarrow{l_1}S_1\xrightarrow{l_2}...S_{n}\xrightarrow{l_{n+1}}S$
  with all $l_k \in L2_{reach}$. In particular, as
  $L2_{reach}\subseteq L2_{sat}$, $l_{n+1} \in L2_{sat}$, meaning it
  it's predicate is satisfiable.

@@

  Conversely if $|S|_{L1_{reach}}=n+1$, we get a similar chain, in
  $L1_{reach}$, with $S_n \xrightarrow{l_{n}}S, S_n \in
  States(L1_{reach})$, and $l_n$ satisfiable. By induction, we have
  $S_n \in States(L2_{reach})=States(L2_{sat})$, so $l_n$ will have
  been checked ``on-the-fly'', in line 6 of algorithm~\ref{alg3}, and
  the OT $S_n \xrightarrow{l_{n}}S$ added to $L2_{sat})$, and we
  conclude $S \in States(L2_{reach})$.

Remember that $L0$ is finite, so we conclude $L1_{reach}=L2_{reach}$, and $States(L1_{reach})=States(L2_{reach})$.

@@

\paragraph{General case with assignments.}
But in the presence of assignments, we need to collect all of them
  before using the assignment information to refine the SAT
  checking. Still, the smart strategy will explore a reduced state
  space, not necessarily the minimal one (discussion later). In the
  following theorem, both algorithm are considered in their complete
  version, meaning the reachability (with assignments) step is
  iterated up to fixpoint.

@@

%\TODO{Formalize the proof}
\begin{proof}
In Theorem 2, we have already proved that the result automata $OA_1$ and $OA_2$ of two algorithms are the same if the pNet contains no assignment to its state variables.

We define the function $States$ as before, and the function $Assignments : \langle OT\rangle\times State\rightarrow\langle Assign\rangle$
computing the set of assignments of a global state from a given set of OTs.

The structure implicitly computed by the algorithm is a triple $ Aut= \langle OTs, States,\\ Assigns\rangle$.

Then the assignments set of $OA_1$ is $\{Assignments(L1, State_{i})\}^{State_{i}\in States(L1)}$ and $OA_2$ is $\{Assignments(L2_{sat}, State_{j})\}^{State_{j}\in States(L2_{sat})}$. The result triples should be 
\[Aut_1 = \langle L1_{sat}, States(L1_{sat}), \{Assignments(L1, State_{i})\}^{State_{i}\in States(L1)}\rangle\] and \[Aut_2 = \langle L2_{sat}, States(L2_{sat}), \{Assignments(L2_{sat}, State_{j})\}^{State_{j}\in States(L2_{sat})}\rangle \ . \]

Basing on the notation of the triple, we define the function $Refine : Aut \rightarrow Aut$ implementing $makeReachableSubAutomaton(S0,OTs)$, it uses the assignments of the previous step to refine the computed reachable space.
\begin{align*}
Refine(Aut) &=\langle L', States(L'), \{Assignments(L', State_{i})\}^{State_{i}\in States(L')}\rangle \\
&=Aut'
\end{align*}
where $L' = L - L_{unsat}$, $L_{unsat}$ is the set of unsatisfiable transitions checked in this iteration. So there must have $|L'|<|L|$, and potentially, their target states and corresponding assignments could be reduced: 
\[States_{L'}=\{State_{init}\}\cup \bigcup States(L'),\]
\[Assignments_{L',States_{L'}}=\bigcup\{Assignments(L', State_{i})\}^{State_{i}\in States_{L'}} \]
\[s.t. |States_{L'}|\le|States_{L}|\wedge|Assignments_{L',States_{L'}}|\le|Assignments_{L,States_{L}}|.\]

@@

\begin{figure}[ht]
\centerline{ 
  \includegraphics[width=0.30\linewidth]{ActaXFIG/Enable1}
  \hspace{25mm}
  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable2}}
  \begin{minipage}{5.7cm}
$  \begin{array}{@{}r@{}l@{}}
    ot_1  = &\openrule{\{ \xrightarrow{a1}_P \},\\ [\forall x1. a1\neq\delta(x1)]}
    {A_0 \xrightarrow{a1} A_0}\\
    ot_2  =& \openrule{
                            \{\xrightarrow{\delta(x2)}_P,\,
                            \xrightarrow{acc(x2)}_Q\}  }
    {A_0 \xrightarrow{\underline{\delta(x2)}} A_1}\\
    ot_3  =& \openrule{
                          \{  \xrightarrow{a3}_q \},\\ [\forall x3. a3\neq\delta(x3)] }
    {A_1 \xrightarrow{a3} A_1}
  \end{array}$
  \end{minipage}
  \hspace{2mm}
  \begin{minipage}{6cm}
$  \begin{array}{@{}r@{}l@{}}
    ot'_1  =& \openrule{
    	\{\xrightarrow{b1}_P\}, ~~ [\forall y1. b1\neq\delta(y1) \!\land\! v=0]}
    {B_0 \xrightarrow{b1} B_0}\\
    ot'_2  =& \openrule{
                            \{\xrightarrow{\delta(y2)}_P,\,
                            \xrightarrow{acc(y2)}_Q \}, \\
                                        v=0, \\
                                        \{v\gets 1\}}
    {B_0 \xrightarrow{\underline{\delta(y2)}} B_1}\\
    ot'_3  =& \openrule{
                            \xrightarrow{b2}_q, \\ [\forall y2. b2\neq\delta(y2) \!\land\! v=1] }
    {B_1 \xrightarrow{b2} B_1}
  \end{array}$
  \end{minipage}
  \caption{The two open automata}
  \label{schema:enable-OAs}
\end{figure}

The open automata generated for the two encodings of Enable in
Figure~\ref{schema:enable-pnets} are displayed in
Figure~\ref{schema:enable-OAs}.
\noteSB{I guess pNets in this figure have to be replaced by open
  automata}
Note that although these automata look very similar to the PLTS
controllers from Figure~\ref{schema:enable-pnets}, their nature is very
different: they represent the behavior of the whole system, including
the holes $P$ and $Q$. Their transitions do not rely on a particular
implementation of the controllers, but only encode the logical
relations between the actions of the holes.
We have shown in \cite{henrio:Forte2016} how to prove these two automata are bisimilar.

@@

\TODO{Simon: reduce...}

@@

Figure~\ref{schema:ArchFailure:pNet} shows a pNet encoding of the
above Failure Monitor architecture.  This encoding is structural: each
coordinator component is encoded as a PLTS; dangling ports belonging
to the operand component are encoded as actions of the hole; 
%%  and the operand component as a hole;
connectors of the BIP model are encoded as synchronisation vectors,
\noteSB{Eric, please check whether this is ok.}\hl{with ports
  representing the actions of the environment used as global actions}.
Each connector that does not involve triggers is trivially encoded by
a synchronisation vector comprising the same ports ($SV2$, $SV3$ and
$SV4$).  In order to encode the semantics of the connectors involving
triggers, we use (in $SV0$ and $SV1$) the classical approach where
non-participation of a port in an interaction is simulated by an
additional loop transition~\cite{milner83-calculi}.  To this end, we
consider an action algebra involving additional Boolean variables: the
effective transitions carry the value $\true$ (\eg $\cstate{0}
\goesto{\PortFail(\true)} \cstate{1}$), whereas the added loops carry
the value $\false$ (\eg $\cstate{2} \goesto{\PortFail(\false)}
\cstate{2}$).  In the synchronisation vectors, we use these variables
to encode the connector structure as a Boolean predicate.  For
example, $SV0$ encodes the connector discussed above: the predicate
$(b1=b2) \land (b1\lor b2 \Rightarrow b0)$ means that the ``true''
transitions $\NameCtrl.\PortFail$ and $\NameTimer.\PortStart$ can only
fire together ($b1 = b2$) and whenever one of them fires,
$\NameOprnd.\PortFail$ must fire also ($b1 \lor b2 \Rightarrow b0$).
This encoding can be systematically obtained for any hierarchical BIP
connector~\cite{BliSif10-causal-fmsd}.
%
%% \noteEM{Decide later if this is still useful}Although, for the sake of
%% brevity, we omit priorities from the encoding, this can be easily
%% achieved, by introducing another set of additional Boolean variables
%% for relevant ports~\cite{BarBliu15-offer-scico}.

@@

For this example, the tool (using Algorithm 1) builds 408 open transitions, whereof 396
are detected unsatisfiable by Z3.  The resulting open automaton, with
3 reachable global states (out of the possible 6) and 12 open
transitions, is shown in Figure~\ref{schema:resultOA1}.\noteSB{Eric, in the state 20, $b0$ should always be $false$: $\PortFail(true)$ is not possible in Control, and the safety property (\ref{eq:FM:safety}) does not hold otherwise.}

@@

	\begin{tabular}{p{4cm}p{3cm}p{3cm}}
		\hline\specialrule{0em}{1pt}{1pt}
		Use-case & Brute force & Smart algorithm
                \\\specialrule{0em}{1pt}{1pt}
		\hline\specialrule{0em}{3pt}{3pt}
		Enable operator   			&
                3/6 OTs           &
                3/6 OTs
                \\\specialrule{0em}{1pt}{1pt} 
                State-based 		&
                125 ms 				&
                110 ms  
		\\\hline\specialrule{0em}{3pt}{3pt}
		Enable operator   			&
                3/6 OTs           &
                3/6 OTs
                \\\specialrule{0em}{1pt}{1pt} 
                Data-based 		&
                141 ms 				&
                205 ms  
		\\\hline\specialrule{0em}{3pt}{3pt}
		Enable Composition   			&
                5/55 OTs           &
                5/42 OTs
                \\\specialrule{0em}{1pt}{1pt} 
                ``P<<(Q<<R)'' State-based		&
                359 ms 				&
                297 ms  
		%% \\\hline\specialrule{0em}{3pt}{3pt}
		%% SimpleProt    			&
                %% 7/260 OTs           &
                %% 7/57 OTs
                %% \\\specialrule{0em}{1pt}{1pt}

                %% (no holes)&
                %% 1536 ms 				&
                %% 359 ms  
%                \\\specialrule{0em}{1pt}{1pt}
%                \textsl{for any sort} & & $=,\ \ne$
		%% \\\hline\specialrule{0em}{1pt}{1pt}
		%% SimpleProt    			&
                %% 19/836 OTs           &
                %% 19/185 OTs
                %% \\\specialrule{0em}{1pt}{1pt}

                %% (with 2 client holes)&
                %% 2496 ms 				&
                %% 844 ms  
		\\\hline\specialrule{0em}{1pt}{1pt}
		FailureTimer    			&
                12/396 OTs           &
                12/192 OTs
                \\\specialrule{0em}{1pt}{1pt} 
  		&
                1220 ms 				&
                687 ms  
		\\\hline\specialrule{0em}{1pt}{1pt}
		FailureTimer X 2    			&
                25/8964 OTs           &
                25/1255 OTs
                \\\specialrule{0em}{1pt}{1pt} 
		&
                18088 ms 				&
                3266 ms  
		\\\hline
	\end{tabular}

@@

\medskip
\begin{theorem}[Finiteness]\cite{henrio:Forte2016}
%\noindent\textbf{Theorem 1} 
	Let $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ be an open pNet  with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
		J}$, where the sets $I$ and $J$ are finite. Suppose the synchronisation vectors of all pNets 
	included in  $pnet$   are finite, and 
	% $\forall i \in L.\, finite{(states(l_i))} \text{ and } l_i$ 
	$l_i $ has a finite number of state variables for each $i\in I$. Then the semantics of $pnet$ is an open automaton 
	%$\mathcal{T}$ 
	with finitely many states and transitions.
\end{theorem}
\begin{proof}
  The possible set of states of the open automaton is the cartesian
  product of the states of the pNet $PLTS_i^{i\in I}$, which is finite by
  hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
  iteration terminates. The enumeration of open-transitions in line 5 of Algorithm~\ref{alg1} is bounded by the
  number of applications of rule Tr2 on the structure of the
  pNet tree. Since a finite number of synchronisation vectors are applied
  at each node, the number of global open transitions is finite. Similarily, if the number
  of transitions of each PLTS is finite, rule Tr1 is 
  applied a finite finite number of times. Therefore, each internal loop of Algorithm~1 terminates, and we obtain finitely many deduction trees and
  open transitions.
  \hfill \qed
  \end{proof}

>>>>

%% When the pNets contains no assignment, there is no need for the last
%% filtering step, so $L1_{sat}=L1_{reach}$ and $L2_{sat}=L2_{reach}$.
We want to prove that $L1_{reach}=L2_{reach}$, that will imply
the equality of the 2 open automata.

\smallskip
Let $S=\ostate{\overline{s}}=\ostate{\{s_{i}\}^{i\in Leaves(pn)}}$
range over the global states $States(L0)$, 
The only difference between the main loops of the algorithms is that 
algorithm~\ref{alg3} only retains the satisfiable OTs (line 6-7), so 
algorithm~\ref{alg3} computes less transitions than
algorithm~\ref{alg1}. Formaly $L2_{reach}\subseteq  L2_{sat} \subseteq L0$, and as a consequence $States(L2_{reach})\subseteq  States(L0)$, so we have:\\
\centerline{$\forall \ostate{\overline{u}}\in States(L2_{reach}), \exists\ostate{\overline{t}}\in States(L0), \ostate{\overline{t}}=\ostate{\overline{u}}$}

@@

\medskip
We will prove by induction on the distance from the original state,
that $\forall S \in L0. \forall n \in \mathbb{N}. S \in States(L2_{reach}) \land |S|_{l2_{reach}}=n => S
\in States(L1_{reach})$, and vice-versa.

  The initial property is trivial, for $n=0$, both state sets of
  distance zero are reduced to $\{S_0\}$.

  Suppose our property is true for distance $n$, and
  suppose $|S|_{L2_{reach}}=n+1$, then there exist a chain
  $S_0\xrightarrow{l_1}S_1\xrightarrow{l_2}...S_{n}\xrightarrow{l_{n+1}}S$
  with all $l_k \in L2_{reach}$. In particular, as
  $L2_{reach}\subseteq L2_{sat}$, $l_{n+1} \in L2_{sat}$, meaning 
  it's predicate is satisfiable.

@@

  Conversely if $|S|_{L1_{reach}}=n+1$, we get a similar chain, in
  $L1_{reach}$, with $S_n \xrightarrow{l_{n}}S, S_n \in
  States(L1_{reach})$, and $l_n$ satisfiable. By induction, we have
  $S_n \in States(L2_{reach})=States(L2_{sat})$, so $l_n$ will have
  been checked ``on-the-fly'', in line 6 of algorithm~\ref{alg3},
  the OT $S_n \xrightarrow{l_{n}}S$ added to $L2_{sat}$, and we
  conclude $S \in States(L2_{reach})$.

Remember $L0$ is finite, so we conclude $L1_{reach}=L2_{reach}$, and $States(L1_{reach})=States(L2_{reach})$.

@@

\paragraph{General case with assignments.}
In the presence of assignments, we need to collect all of them
  before using the assignment information to refine the SAT
  checking. Still, the smart strategy will explore a reduced state
  space, not necessarily the minimal one. In the
  following theorem, both algorithms are considered in their complete
  version, meaning the reachability (with assignments) step is
  iterated up to fixpoint.

@@

%\TODO{Formalize the proof}
\begin{proof}
  Define the OT sets $L0, L1_{sat}, L2_{sat}, L2_{reach}$ as previously, and:

  \begin{itemize}
    \item $L1_{reach*}$ = final set of OTs of Algorithm 1, as computed
        by an iterative application of makeReachableSubAutomaton (line
        14) up to fixpoint.
      \item $L2_{reach*}$ = final set of OTs of Algorithm 2, as computed
        by an iterative application of makeReachableSubAutomaton (line
        16) up to fixpoint.
  \end{itemize}

?? In Theorem 2, we have already proved that the result automata $OA_1$ and $OA_2$ of two algorithms are the same if the pNet contains no assignment to its state variables.

We define the function $States$ as before, and the function $Assignments : \overline{OT}\ \times State\rightarrow \overline{Assign}$
computing the set of assignments of a global state from a given set of OTs.

The structure implicitly computed by both algorithms is a triple $ Aut= \langle \overline{OT}, \overline{State},\\ \overline{Assign}\rangle$.

Then the assignments set of $OA_1$ is $\{Assignments(L1, S_i)\}^{S_i\in States(L1)}$ and $OA_2$ is $\{Assignments(L2_{sat}, S_j)\}^{S_j\in States(L2_{sat})}$. The result triples are:  
\noindent
\begin{align*}
Aut_1 = \langle L1_{sat}, States(L1_{sat}), \{Assignments(L1, S_i)\}^{S_i\in States(L1)}\rangle\\
Aut_2 = \langle L2_{sat}, States(L2_{sat}), \{Assignments(L2_{sat}, S_j)\}^{S_j\in States(L2_{sat})}\rangle \ 
\end{align*}

Based on this triple structure, we define the function $Refine : Aut \rightarrow Aut$ modeling $makeReachableSubAutomaton(S0,OTs)$. It uses the assignments of the previous step to refine the computed reachable space:
\begin{align*}
Refine(Aut) &=\langle L', States(L'), \{Assignments(L', S_i)\}^{S_i\in States(L')}\rangle \\
&=Aut'
\end{align*}
where $L' = L - L_{unsat}$, and $L_{unsat}$ is the set of unsatisfiable transitions checked in this iteration. We have $L'\subseteq L$, and potentially, their target states and corresponding assignments may be reduced: 
\[States(L')=\{S_0\}\cup \bigcup States(L'),\]
\[Assignments_{L',States_{L'}}=\bigcup\{Assignments(L', State_{i})\}^{State_{i}\in States_{L'}} \]
\[s.t. |States_{L'}|\le|States_{L}|\wedge|Assignments_{L',States_{L'}}|\le|Assignments_{L,States_{L}}|.\]

@@

\begin{figure}[ht]
\centerline{ 
  \includegraphics[width=0.30\linewidth]{ActaXFIG/Enable1-aut}
  \hspace{25mm}
  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable2-aut}}
  \begin{minipage}{5.7cm}
$  \begin{array}{@{}r@{}l@{}}
    ot_1  = &\openrule{\{ \xrightarrow{a1}_P \},\\ [\forall x1. a1\neq\delta(x1)]}
    {A_0 \xrightarrow{a1} A_0}\\
    ot_2  =& \openrule{
                            \{\xrightarrow{\delta(x2)}_P,\,
                            \xrightarrow{acc(x2)}_Q\}  }
    {A_0 \xrightarrow{\underline{\delta(x2)}} A_1}\\
    ot_3  =& \openrule{
                          \{  \xrightarrow{a3}_q \},\\ [\forall x3. a3\neq\delta(x3)] }
    {A_1 \xrightarrow{a3} A_1}
  \end{array}$
  \end{minipage}
  \hspace{2mm}
  \begin{minipage}{6cm}
$  \begin{array}{@{}r@{}l@{}}
    ot'_1  =& \openrule{
    	\{\xrightarrow{b1}_P\}, ~~ [\forall y1. b1\neq\delta(y1) \!\land\! v=0]}
    {B_0 \xrightarrow{b1} B_0}\\
    ot'_2  =& \openrule{
                            \{\xrightarrow{\delta(y2)}_P,\,
                            \xrightarrow{acc(y2)}_Q \}, \\
                                        v=0, \\
                                        \{v\gets 1\}}
    {B_0 \xrightarrow{\underline{\delta(y2)}} B_1}\\
    ot'_3  =& \openrule{
                            \xrightarrow{b2}_q, \\ [\forall y2. b2\neq\delta(y2) \!\land\! v=1] }
    {B_1 \xrightarrow{b2} B_1}
  \end{array}$
  \end{minipage}
  \caption{The two open automata}
  \label{schema:enable-OAs}
\end{figure}

The open automata generated for the two encodings of Enable in
Figure~\ref{schema:enable-pnets} are displayed in
Figure~\ref{schema:enable-OAs}.
Note that although these automata look very similar to the PLTS
controllers from Figure~\ref{schema:enable-pnets}, their nature is very
different: they represent the behavior of the whole system, including
the holes $P$ and $Q$. Their transitions do not rely on a particular
implementation of the controllers, but only encode the logical
relations between the actions of the holes.
We have shown in \cite{henrio:Forte2016} how to prove these two automata are bisimilar.

@@

@@

Figure~\ref{schema:ArchFailure:pNet} shows a pNet encoding of the
above Failure Monitor architecture.  This encoding is structural: each
coordinator component is encoded as a PLTS; dangling ports belonging
to the operand component are encoded as actions of the hole; 
%%  and the operand component as a hole;
connectors of the BIP model are encoded as synchronisation vectors,
with ports
  representing the actions of the environment used as global actions.
Each connector that does not involve triggers is trivially encoded by
a synchronisation vector comprising the same ports ($SV2$, $SV3$ and
$SV4$).  In order to encode the semantics of the connectors involving
triggers, we use (in $SV0$ and $SV1$) the classical approach where
non-participation of a port in an interaction is simulated by an
additional loop transition~\cite{milner83-calculi}.  To this end, we
consider an action algebra involving additional Boolean variables: the
effective transitions carry the value $\true$ (\eg $\cstate{0}
\goesto{\PortFail(\true)} \cstate{1}$), whereas the added loops carry
the value $\false$ (\eg $\cstate{2} \goesto{\PortFail(\false)}
\cstate{2}$).  In the synchronisation vectors, we use these variables
to encode the connector structure as a Boolean predicate.  For
example, $SV0$ encodes the connector discussed above: the predicate
$(b1=b2) \land (b1\lor b2 \Rightarrow b0)$ means that the ``true''
transitions $\NameCtrl.\PortFail$ and $\NameTimer.\PortStart$ can only
fire together ($b1 = b2$) and whenever one of them fires,
$\NameOprnd.\PortFail$ must fire also ($b1 \lor b2 \Rightarrow b0$).
This encoding can be systematically obtained for any hierarchical BIP
connector~\cite{BliSif10-causal-fmsd}.
%
%% \noteEM{Decide later if this is still useful}Although, for the sake of
%% brevity, we omit priorities from the encoding, this can be easily
%% achieved, by introducing another set of additional Boolean variables
%% for relevant ports~\cite{BarBliu15-offer-scico}.

@@

For this example, the tool (using Algorithm 1) builds 408 open transitions, whereof 396
are detected unsatisfiable by Z3.  The resulting open automaton, with
3 reachable global states (out of the possible 6) and 12 open
transitions, is shown in Figure~\ref{schema:resultOA1}.
%% \noteSB{Eric, in the state 20, $b0$ should always be $false$: $\PortFail(true)$ is not possible in Control, and the safety property (\ref{eq:FM:safety}) does not hold otherwise.}

@@

	\begin{tabular}{p{4cm}p{3cm}p{3cm}}
		\hline\specialrule{0em}{1pt}{1pt}
		Use-case & Brute force & Smart algorithm
                \\\specialrule{0em}{1pt}{1pt}
		\hline\specialrule{0em}{3pt}{3pt}
		Enable operator   			&
                3/6 OTs           &
                3/6 OTs
                \\\specialrule{0em}{1pt}{1pt} 
                State-based 		&
                125 ms 				&
                110 ms  
		\\\hline\specialrule{0em}{3pt}{3pt}
		Enable operator   			&
                3/6 OTs           &
                3/6 OTs
                \\\specialrule{0em}{1pt}{1pt} 
                Data-based 		&
                141 ms 				&
                205 ms  
		\\\hline\specialrule{0em}{3pt}{3pt}
		Enable Composition   			&
                5/55 OTs           &
                5/42 OTs
                \\\specialrule{0em}{1pt}{1pt} 
                ``P<<(Q<<R)'' State-based		&
                359 ms 				&
                297 ms  
		\\\hline\specialrule{0em}{1pt}{1pt}
		FailureTimer    			&
                12/396 OTs           &
                12/192 OTs
                \\\specialrule{0em}{1pt}{1pt} 
  		&
                1220 ms 				&
                687 ms  
		\\\hline\specialrule{0em}{1pt}{1pt}
		FailureTimer X 2    			&
                25/8964 OTs           &
                25/1255 OTs
                \\\specialrule{0em}{1pt}{1pt} 
		&
                18088 ms 				&
                3266 ms  
		\\\hline
	\end{tabular}

@@

\medskip
\begin{theorem}[Finiteness]\cite{henrio:Forte2016}
%\noindent\textbf{Theorem 1} 
	Let $pnet=\mylangle \overline{\pNet},\overline{S}, \symb{SV}_k^{k\in K}\myrangle$ be an open pNet  with leaves $l_i^{i\in I}$ and holes $h_j^{j\in
		J}$, where the sets $I$ and $J$ are finite. Suppose the synchronisation vectors of all pNets 
	included in  $pnet$   are finite, and 
	% $\forall i \in L.\, finite{(states(l_i))} \text{ and } l_i$ 
	$l_i $ has a finite number of state variables for each $i\in I$. Then the semantics of $pnet$ is an open automaton 
	%$\mathcal{T}$ 
	with finitely many states and transitions.
\end{theorem}
\begin{proof}
  The possible set of states of the open automaton is the cartesian
  product of the states of the pNet $PLTS_i^{i\in I}$, which is finite by
  hypothesis. So the top-level residual loop of Algorithm 1 terminates provided each 
  iteration terminates. The enumeration of open-transitions in line 5 of Algorithm~\ref{alg1} is bounded by the
  number of applications of rule Tr2 on the structure of the
  pNet tree. Since a finite number of synchronisation vectors are applied
  at each node, the number of global open transitions is finite. Similarily, if the number
  of transitions of each PLTS is finite, rule Tr1 is 
  applied a finite number of times. Therefore, each internal loop of Algorithm~1 terminates, and we obtain finitely many deduction trees and
  open transitions.
  \hfill \qed
  \end{proof}
